---
title: "exercise#1"
output:
  pdf_document: default
  html_document: default
date: "2024-03-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
A.Load the built-in warpbreaks dataset.
```{r}
data("warpbreaks")
warpbreaks
```
A1.Find out, in a single command, which columns of warpbreaks are either numeric or
integer. What are the data types of each column?
```{r}
str(warpbreaks)
```
A2.How many observations does it have?
```{r}
#it has 54 observations.
```
A3.Is numeric a natural data type for the columns which are stored as such? Convert to
integer when necessary.
```{r}
typeof(warpbreaks$breaks)
typeof(warpbreaks$wool)
typeof(warpbreaks$tension)
#new

#the data type of breaks, wool, and tension is double, integer, and integer.
```
A4.Error messages in R sometimes report the underlying type of an object rather than the
user-level class. Derive from the following code and error message what the
underlying type. Explain what is the error all about. Do not just copy the error
message that was displayed.
```{r}

```
B.Load the exampleFile.txt
B1.Read the complete file using readLines.
```{r}
file <- file("exampleFile.txt")

fileread <- readLines(file)
fileread
```
B2.Separate the vector of lines into a vector containing comments and a vector
containing the data. Hint: use grepl.
```{r}
comments <- fileread[grepl("^//", fileread)]
comments

datavector <- fileread[!grepl("^//", fileread)]
datavector
```
B3.Extract the date from the first comment line and display on the screen “It was created
data.”
```{r}
subcomments <- comments[1]
date <- gsub("// Survey data. Created : ", "", subcomments)
date

cat("It was created, ", date)
```
B4.
B4a.Split the character vectors in the vector containing data lines by semicolon (;)
using strsplit.
```{r}
vectorsplit <- (strsplit(datavector, ";"))
vectorsplit
```
B4b.Find the maximum number of fields retrieved by split. Append rows that are
shorter with NA's.
```{r}

maxvector <- max(lengths(vectorsplit))
maxvector

rowappend <- lapply(vectorsplit, function(x) c(x, rep(NA, maxvector - length(x))))
rowappend
```
B4c.Use unlist and matrix to transform the data to row-column format.
```{r}

unlistdata <- unlist(rowappend)
unlistdata

datamatrix <- matrix(unlistdata, ncol = 4, nrow=3,
                     dimnames = list(c("row1","row2", "row3")))
datamatrix
```
B5d.From comment lines 2-4, extract the names of the fields. Set these as
colnames for the matrix you just created.
```{r}
fieldnames <- comments[2:4]
extfieldname <- gsub("//", "", fieldnames)
extfieldname
rownames(datamatrix) <- extfieldname
datamatrix

```











